# Functions

These functions essentially repeat the previous steps from the example model, but allow us to repeat the process for all combinations of handedness, pitch type, and count. The parameters can be inputted into the functions to give us a resulting data frame and plot to visualize for each unique combination of handedness, count, and pitch type.


## Function 1

```{r}
function_p_type_hand_ptiles <- function(df, hand, pitch_type) {
  hand = enquo(hand)
  pitch_type = enquo(pitch_type)
  hand_pitch_df <- df %>% filter(UQ(hand) == hand, UQ(pitch_type) == pitch_type)

  gf <- gam(re ~ s(x, y), data = hand_pitch_df)
}
```

## Function 2

```{r}
location_quality <- function(df, hand, pitch_type, count, gf) {
  
  hand = enquo(hand)
  pitch_type = enquo(pitch_type)
  count = enquo(count)
  count_df <- df %>% filter(UQ(count) == count)
  hand_pitch_df <- df %>% filter(UQ(hand) == hand, UQ(pitch_type) == pitch_type)
  hand_pitch_count_df <- df %>% filter(UQ(hand) == hand, UQ(pitch_type) == pitch_type, UQ(count) == count)
  hand_count_df <- df %>% filter(UQ(hand) == hand, UQ(count) == count)
  
  n <- hand_pitch_count_df %>% count() %>% as_vector()
  
  if (n > 20000) {
    hand_pitch_count_df <- hand_pitch_count_df %>% slice_sample(n=20000)
    } else {
      hand_pitch_count_df
    }
  
g <- expand.grid(x = seq(-4, 4, 0.01), y = seq(-2, 6, 0.01)) %>% 
  mutate(x=round(x,2), y=round(y,2)) %>% 
  as_tibble()
  
#gf <- gam(re ~ s(x, y), data = hand_pitch_df)
  
gfa <- gf %>% augment()
  
gfa99 <- gfa %>% 
  filter(.hat <= quantile(gfa$.hat, 0.99)) %>% 
  select(x, y)

aa <- gfa99 %>% group_by(x) %>% summarise(ymin=min(y), ymax=max(y))

bb <- inner_join(g,aa, join_by(x==x, y>=ymin, y<=ymax)) %>% select(-y) %>% distinct()

cc <- g %>% left_join(bb, join_by(x==x, y>=ymin, y<=ymax)) %>% 
  filter(!is.na(ymin), !is.na(ymax)) %>% select(x,y)

dd <- cc %>% group_by(y) %>% summarise(xmin=min(x), xmax=max(x))

ee <- inner_join(g,dd, join_by(y==y, x>=xmin, x<=xmax)) %>% select(-x) %>% distinct()

ff <- g %>% left_join(ee, join_by(y==y, x>=xmin, x<=xmax)) %>% 
  filter(!is.na(xmin), !is.na(xmax)) %>% select(x,y)

gg <- bind_rows(cc,ff) %>% distinct()

aa <- gg %>% group_by(x) %>% summarise(ymin=min(y), ymax=max(y))

bb <- inner_join(g,aa, join_by(x==x, y>=ymin, y<=ymax)) %>% select(-y) %>% distinct()

cc <- g %>% left_join(bb, join_by(x==x, y>=ymin, y<=ymax)) %>% 
  filter(!is.na(ymin), !is.na(ymax)) %>% select(x,y)

dd <- cc %>% group_by(y) %>% summarise(xmin=min(x), xmax=max(x))

ee <- inner_join(g,dd, join_by(y==y, x>=xmin, x<=xmax)) %>% select(-x) %>% distinct()

ff <- g %>% left_join(ee, join_by(y==y, x>=xmin, x<=xmax)) %>% 
  filter(!is.na(xmin), !is.na(xmax)) %>% select(x,y)

gg <- bind_rows(cc,ff) %>% distinct()

gf1 <- gam(re ~ s(x, y), data = hand_pitch_count_df, method = "REML")
  
gg$lp <- predict(gf1, gg, type = "response")

gg <- gg %>%
  mutate(hand = unique(hand_pitch_count_df$hand),
         pitch_type = unique(hand_pitch_count_df$pitch_type),
         count = unique(hand_pitch_count_df$count)) %>%
  select(hand, pitch_type, count, x, y, lp)

gg <- gg %>% mutate(pq = (lp - min(lp)) / (max(lp) - min(lp))) %>% select(-lp) %>%
  mutate(pq = 1-pq)

return(gg)
}
```

## Function 3

```{r}
location_quality_plot <- function(df) {
  
    hand <- tibble(hand_id = c(1,2,3,4), hand = c("RvR","RvL","LvL","LvR"))
    pitch_type <- tibble(pitch_type_id = c(1,2,3,4,5,6), 
                         pitch_type = c("FF","SI","FC","CH","CU","SL"))
    count <- tibble(count_id = c(1,2,3,4,5,6,7,8,9,10,11,12), 
                    count = c("0-0","0-1","0-2","1-0","1-1","1-2","2-0","2-1","2-2","3-0","3-1","3-2"))

  df <- df %>%
    inner_join(hand, join_by(hand==hand_id)) %>%
    select(-hand) %>%
    rename(hand=hand.y) %>%
    inner_join(pitch_type, join_by(pitch_type==pitch_type_id)) %>%
    select(-pitch_type) %>%
    rename(pitch_type=pitch_type.y) %>%
    inner_join(count, join_by(count==count_id)) %>%
    select(-count) %>%
    rename(count=count.y)
  
  rm(hand, pitch_type, count)
  
  df <- df %>% mutate(label = paste(hand, pitch_type, count, sep = " "))
    ggplot() +
      geom_tile(data= df, aes(x,y, fill = pq), show.legend = FALSE) +
      geom_rect(aes(ymax = 3.50, ymin = 1.5, xmax = 0.83, xmin = -0.83),
                alpha = 0, linewidth=0.1, colour = "red") +
      ggtitle(unique(df$label)) +
      theme_bw() + 
      scale_fill_viridis_c(direction = 1, limits = c(0,1)) +
      theme(axis.title = element_blank(),
            plot.title = element_text(hjust = 0.5, size = 12),
            panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank())+
      coord_fixed()
}
```
