# Applying Functions

There are 288 unique combinations of handedness, pitch type, and count. Each combination will get its own GAM smooth. Running this code takes considerable processing time, so to speed up the process I'll convert the category values of the mlbraw2 data frame to integers with indexed values. Then after the computations are complete, I'll convert the integer values back to the original categorical values.

The result of all this computation will be 288 data frames each with every possible combination of x and y value from its grid plot. For example, the grid region representing 99% of all sliders thrown RHP to RHB will have every possible combination of x and y value in it. Along with x and y values with its corresponding change in run expectancy as visualized before.

All 288 data frames will be compiled together into a single data frame to be used to join to a season's worth of data.

## Create Data Frames

```{r data type transformation}
hand <- tibble(hand_id = c(1,2,3,4), hand = c("RvR","RvL","LvL","LvR"))
pitch_type <- tibble(pitch_type_id = c(1,2,3,4,5,6), 
                     pitch_type = c("FF","SI","FC","CH","CU","SL"))
count <- tibble(count_id = c(1,2,3,4,5,6,7,8,9,10,11,12), 
                count = c("0-0","0-1","0-2","1-0","1-1","1-2","2-0","2-1","2-2","3-0","3-1","3-2"))
events <- tibble(events_id = c(1,2,3,4,5,6,7,8,9) ,
                 events = c("ball","double","hr","out","single","strike","triple","foul","walk"))

mlbraw2 <- mlbraw2 %>%
  inner_join(hand, join_by(hand)) %>%
  select(-hand) %>%
  rename(hand=hand_id) %>%
  inner_join(pitch_type, join_by(pitch_type)) %>%
  select(-pitch_type) %>%
  rename(pitch_type=pitch_type_id) %>%
  inner_join(count, join_by(count)) %>%
  select(-count) %>%
  rename(count=count_id) %>%
  inner_join(events, join_by(events)) %>%
  select(-events) %>%
  rename(events=events_id)

mlbraw2$hand <- as.integer(as.factor(mlbraw2$hand))
mlbraw2$pitch_type <- as.integer(as.factor(mlbraw2$pitch_type))
mlbraw2$count <- as.integer(as.factor(mlbraw2$count))
mlbraw2$events <- as.integer(as.factor(mlbraw2$events))

rm(hand, pitch_type, count, events)
```

```{r function_p_type_hand_ptiles}
gf_r_r_ff <- function_p_type_hand_ptiles(mlbraw2, 1, 1) # "RvR", "SI"
gf_r_r_si <- function_p_type_hand_ptiles(mlbraw2, 1, 2) # "RvR", "SI"
gf_r_r_fc <- function_p_type_hand_ptiles(mlbraw2, 1, 3) # "RvR", "FC"
gf_r_r_ch <- function_p_type_hand_ptiles(mlbraw2, 1, 4) # "RvR", "CH"
gf_r_r_cu <- function_p_type_hand_ptiles(mlbraw2, 1, 5) # "RvR", "CU"
gf_r_r_sl <- function_p_type_hand_ptiles(mlbraw2, 1, 6) # "RvR", "SL"

gf_r_l_ff <- function_p_type_hand_ptiles(mlbraw2, 2, 1) # "RvL", "FF"
gf_r_l_si <- function_p_type_hand_ptiles(mlbraw2, 2, 2) # "RvL", "SI"
gf_r_l_fc <- function_p_type_hand_ptiles(mlbraw2, 2, 3) # "RvL", "FC"
gf_r_l_ch <- function_p_type_hand_ptiles(mlbraw2, 2, 4) # "RvL", "CH"
gf_r_l_cu <- function_p_type_hand_ptiles(mlbraw2, 2, 5) # "RvL", "CU"
gf_r_l_sl <- function_p_type_hand_ptiles(mlbraw2, 2, 6) # "RvL", "SL"

gf_l_l_ff <- function_p_type_hand_ptiles(mlbraw2, 3, 1) # "LvL", "FF"
gf_l_l_si <- function_p_type_hand_ptiles(mlbraw2, 3, 2) # "LvL", "SI"
gf_l_l_fc <- function_p_type_hand_ptiles(mlbraw2, 3, 3) # "LvL", "FC"
gf_l_l_ch <- function_p_type_hand_ptiles(mlbraw2, 3, 4) # "LvL", "CH"
gf_l_l_cu <- function_p_type_hand_ptiles(mlbraw2, 3, 5) # "LvL", "CU"
gf_l_l_sl <- function_p_type_hand_ptiles(mlbraw2, 3, 6) # "LvL", "SL"

gf_l_r_ff <- function_p_type_hand_ptiles(mlbraw2, 4, 1) # "LvR", "FF")
gf_l_r_si <- function_p_type_hand_ptiles(mlbraw2, 4, 2) # "LvR", "SI")
gf_l_r_fc <- function_p_type_hand_ptiles(mlbraw2, 4, 3) # "LvR", "FC")
gf_l_r_ch <- function_p_type_hand_ptiles(mlbraw2, 4, 4) # "LvR", "CH")
gf_l_r_cu <- function_p_type_hand_ptiles(mlbraw2, 4, 5) # "LvR", "CU")
gf_l_r_sl <- function_p_type_hand_ptiles(mlbraw2, 4, 6) # "LvR", "SL")
```

```{r r_r_ff}
r_r_ff_0_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 1, count = 1, gf = gf_r_r_ff)
r_r_ff_0_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 1, count = 2, gf = gf_r_r_ff)
r_r_ff_0_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 1, count = 3, gf = gf_r_r_ff)
r_r_ff_1_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 1, count = 4, gf = gf_r_r_ff)
r_r_ff_1_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 1, count = 5, gf = gf_r_r_ff)
r_r_ff_1_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 1, count = 6, gf = gf_r_r_ff)
r_r_ff_2_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 1, count = 7, gf = gf_r_r_ff)
r_r_ff_2_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 1, count = 8, gf = gf_r_r_ff)
r_r_ff_2_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 1, count = 9, gf = gf_r_r_ff)
r_r_ff_3_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 1, count = 10, gf = gf_r_r_ff)
r_r_ff_3_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 1, count = 11, gf = gf_r_r_ff)
r_r_ff_3_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 1, count = 12, gf = gf_r_r_ff)
```

```{r r_r_si}
r_r_si_0_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 2, count = 1, gf = gf_r_r_si)
r_r_si_0_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 2, count = 2, gf = gf_r_r_si)
r_r_si_0_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 2, count = 3, gf = gf_r_r_si)
r_r_si_1_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 2, count = 4, gf = gf_r_r_si)
r_r_si_1_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 2, count = 5, gf = gf_r_r_si)
r_r_si_1_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 2, count = 6, gf = gf_r_r_si)
r_r_si_2_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 2, count = 7, gf = gf_r_r_si)
r_r_si_2_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 2, count = 8, gf = gf_r_r_si)
r_r_si_2_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 2, count = 9, gf = gf_r_r_si)
r_r_si_3_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 2, count = 10, gf = gf_r_r_si)
r_r_si_3_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 2, count = 11, gf = gf_r_r_si)
r_r_si_3_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 2, count = 12, gf = gf_r_r_si)
```

```{r r_r_fc}
r_r_fc_0_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 3, count = 1, gf = gf_r_r_fc)
r_r_fc_0_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 3, count = 2, gf = gf_r_r_fc)
r_r_fc_0_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 3, count = 3, gf = gf_r_r_fc)
r_r_fc_1_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 3, count = 4, gf = gf_r_r_fc)
r_r_fc_1_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 3, count = 5, gf = gf_r_r_fc)
r_r_fc_1_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 3, count = 6, gf = gf_r_r_fc)
r_r_fc_2_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 3, count = 7, gf = gf_r_r_fc)
r_r_fc_2_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 3, count = 8, gf = gf_r_r_fc)
r_r_fc_2_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 3, count = 9, gf = gf_r_r_fc)
r_r_fc_3_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 3, count = 10, gf = gf_r_r_fc)
r_r_fc_3_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 3, count = 11, gf = gf_r_r_fc)
r_r_fc_3_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 3, count = 12, gf = gf_r_r_fc)
```

```{r r_r_ch}
r_r_ch_0_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 4, count = 1, gf = gf_r_r_ch)
r_r_ch_0_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 4, count = 2, gf = gf_r_r_ch)
r_r_ch_0_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 4, count = 3, gf = gf_r_r_ch)
r_r_ch_1_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 4, count = 4, gf = gf_r_r_ch)
r_r_ch_1_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 4, count = 5, gf = gf_r_r_ch)
r_r_ch_1_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 4, count = 6, gf = gf_r_r_ch)
r_r_ch_2_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 4, count = 7, gf = gf_r_r_ch)
r_r_ch_2_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 4, count = 8, gf = gf_r_r_ch)
r_r_ch_2_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 4, count = 9, gf = gf_r_r_ch)
r_r_ch_3_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 4, count = 10, gf = gf_r_r_ch)
r_r_ch_3_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 4, count = 11, gf = gf_r_r_ch)
r_r_ch_3_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 4, count = 12, gf = gf_r_r_ch)

```

```{r r_r_sl}
r_r_sl_0_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 6, count = 1, gf = gf_r_r_sl)
r_r_sl_0_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 6, count = 2, gf = gf_r_r_sl)
r_r_sl_0_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 6, count = 3, gf = gf_r_r_sl)
r_r_sl_1_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 6, count = 4, gf = gf_r_r_sl)
r_r_sl_1_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 6, count = 5, gf = gf_r_r_sl)
r_r_sl_1_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 6, count = 6, gf = gf_r_r_sl)
r_r_sl_2_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 6, count = 7, gf = gf_r_r_sl)
r_r_sl_2_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 6, count = 8, gf = gf_r_r_sl)
r_r_sl_2_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 6, count = 9, gf = gf_r_r_sl)
r_r_sl_3_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 6, count = 10, gf = gf_r_r_sl)
r_r_sl_3_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 6, count = 11, gf = gf_r_r_sl)
r_r_sl_3_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 6, count = 12, gf = gf_r_r_sl)
```

```{r r_r_cu}
r_r_cu_0_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 5, count = 1, gf = gf_r_r_cu)
r_r_cu_0_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 5, count = 2, gf = gf_r_r_cu)
r_r_cu_0_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 5, count = 3, gf = gf_r_r_cu)
r_r_cu_1_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 5, count = 4, gf = gf_r_r_cu)
r_r_cu_1_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 5, count = 5, gf = gf_r_r_cu)
r_r_cu_1_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 5, count = 6, gf = gf_r_r_cu)
r_r_cu_2_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 5, count = 7, gf = gf_r_r_cu)
r_r_cu_2_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 5, count = 8, gf = gf_r_r_cu)
r_r_cu_2_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 5, count = 9, gf = gf_r_r_cu)
r_r_cu_3_0 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 5, count = 10, gf = gf_r_r_cu)
r_r_cu_3_1 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 5, count = 11, gf = gf_r_r_cu)
r_r_cu_3_2 <- location_quality(df = mlbraw2, hand = 1, pitch_type = 5, count = 12, gf = gf_r_r_cu)
```

```{r r_l_ff}
r_l_ff_0_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 1, count = 1, gf = gf_r_l_ff)
r_l_ff_0_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 1, count = 2, gf = gf_r_l_ff)
r_l_ff_0_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 1, count = 3, gf = gf_r_l_ff)
r_l_ff_1_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 1, count = 4, gf = gf_r_l_ff)
r_l_ff_1_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 1, count = 5, gf = gf_r_l_ff)
r_l_ff_1_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 1, count = 6, gf = gf_r_l_ff)
r_l_ff_2_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 1, count = 7, gf = gf_r_l_ff)
r_l_ff_2_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 1, count = 8, gf = gf_r_l_ff)
r_l_ff_2_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 1, count = 9, gf = gf_r_l_ff)
r_l_ff_3_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 1, count = 10, gf = gf_r_l_ff)
r_l_ff_3_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 1, count = 11, gf = gf_r_l_ff)
r_l_ff_3_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 1, count = 12, gf = gf_r_l_ff)
```

```{r r_l_si}
r_l_si_0_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 2, count = 1, gf = gf_r_l_si)
r_l_si_0_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 2, count = 2, gf = gf_r_l_si)
r_l_si_0_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 2, count = 3, gf = gf_r_l_si)
r_l_si_1_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 2, count = 4, gf = gf_r_l_si)
r_l_si_1_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 2, count = 5, gf = gf_r_l_si)
r_l_si_1_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 2, count = 6, gf = gf_r_l_si)
r_l_si_2_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 2, count = 7, gf = gf_r_l_si)
r_l_si_2_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 2, count = 8, gf = gf_r_l_si)
r_l_si_2_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 2, count = 9, gf = gf_r_l_si)
r_l_si_3_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 2, count = 10, gf = gf_r_l_si)
r_l_si_3_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 2, count = 11, gf = gf_r_l_si)
r_l_si_3_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 2, count = 12, gf = gf_r_l_si)
```

```{r r_l_fc}
r_l_fc_0_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 3, count = 1, gf = gf_r_l_fc)
r_l_fc_0_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 3, count = 2, gf = gf_r_l_fc)
r_l_fc_0_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 3, count = 3, gf = gf_r_l_fc)
r_l_fc_1_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 3, count = 4, gf = gf_r_l_fc)
r_l_fc_1_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 3, count = 5, gf = gf_r_l_fc)
r_l_fc_1_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 3, count = 6, gf = gf_r_l_fc)
r_l_fc_2_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 3, count = 7, gf = gf_r_l_fc)
r_l_fc_2_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 3, count = 8, gf = gf_r_l_fc)
r_l_fc_2_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 3, count = 9, gf = gf_r_l_fc)
r_l_fc_3_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 3, count = 10, gf = gf_r_l_fc)
r_l_fc_3_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 3, count = 11, gf = gf_r_l_fc)
r_l_fc_3_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 3, count = 12, gf = gf_r_l_fc)
```

```{r r_l_ch}
r_l_ch_0_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 4, count = 1, gf = gf_r_l_ch)
r_l_ch_0_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 4, count = 2, gf = gf_r_l_ch)
r_l_ch_0_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 4, count = 3, gf = gf_r_l_ch)
r_l_ch_1_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 4, count = 4, gf = gf_r_l_ch)
r_l_ch_1_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 4, count = 5, gf = gf_r_l_ch)
r_l_ch_1_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 4, count = 6, gf = gf_r_l_ch)
r_l_ch_2_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 4, count = 7, gf = gf_r_l_ch)
r_l_ch_2_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 4, count = 8, gf = gf_r_l_ch)
r_l_ch_2_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 4, count = 9, gf = gf_r_l_ch)
r_l_ch_3_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 4, count = 10, gf = gf_r_l_ch)
r_l_ch_3_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 4, count = 11, gf = gf_r_l_ch)
r_l_ch_3_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 4, count = 12, gf = gf_r_l_ch)

```

```{r r_l_sl}
r_l_sl_0_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 6, count = 1, gf = gf_r_l_sl)
r_l_sl_0_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 6, count = 2, gf = gf_r_l_sl)
r_l_sl_0_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 6, count = 3, gf = gf_r_l_sl)
r_l_sl_1_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 6, count = 4, gf = gf_r_l_sl)
r_l_sl_1_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 6, count = 5, gf = gf_r_l_sl)
r_l_sl_1_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 6, count = 6, gf = gf_r_l_sl)
r_l_sl_2_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 6, count = 7, gf = gf_r_l_sl)
r_l_sl_2_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 6, count = 8, gf = gf_r_l_sl)
r_l_sl_2_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 6, count = 9, gf = gf_r_l_sl)
r_l_sl_3_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 6, count = 10, gf = gf_r_l_sl)
r_l_sl_3_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 6, count = 11, gf = gf_r_l_sl)
r_l_sl_3_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 6, count = 12, gf = gf_r_l_sl)
```

```{r r_l_cu}
r_l_cu_0_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 5, count = 1, gf = gf_r_l_cu)
r_l_cu_0_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 5, count = 2, gf = gf_r_l_cu)
r_l_cu_0_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 5, count = 3, gf = gf_r_l_cu)
r_l_cu_1_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 5, count = 4, gf = gf_r_l_cu)
r_l_cu_1_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 5, count = 5, gf = gf_r_l_cu)
r_l_cu_1_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 5, count = 6, gf = gf_r_l_cu)
r_l_cu_2_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 5, count = 7, gf = gf_r_l_cu)
r_l_cu_2_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 5, count = 8, gf = gf_r_l_cu)
r_l_cu_2_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 5, count = 9, gf = gf_r_l_cu)
r_l_cu_3_0 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 5, count = 10, gf = gf_r_l_cu)
r_l_cu_3_1 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 5, count = 11, gf = gf_r_l_cu)
r_l_cu_3_2 <- location_quality(df = mlbraw2, hand = 2, pitch_type = 5, count = 12, gf = gf_r_l_cu)
```

```{r l_l_ff}
l_l_ff_0_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 1, count = 1, gf = gf_l_l_ff)
l_l_ff_0_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 1, count = 2, gf = gf_l_l_ff)
l_l_ff_0_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 1, count = 3, gf = gf_l_l_ff)
l_l_ff_1_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 1, count = 4, gf = gf_l_l_ff)
l_l_ff_1_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 1, count = 5, gf = gf_l_l_ff)
l_l_ff_1_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 1, count = 6, gf = gf_l_l_ff)
l_l_ff_2_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 1, count = 7, gf = gf_l_l_ff)
l_l_ff_2_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 1, count = 8, gf = gf_l_l_ff)
l_l_ff_2_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 1, count = 9, gf = gf_l_l_ff)
l_l_ff_3_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 1, count = 10, gf = gf_l_l_ff)
l_l_ff_3_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 1, count = 11, gf = gf_l_l_ff)
l_l_ff_3_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 1, count = 12, gf = gf_l_l_ff)
```

```{r l_l_si}
l_l_si_0_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 2, count = 1, gf = gf_l_l_si)
l_l_si_0_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 2, count = 2, gf = gf_l_l_si)
l_l_si_0_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 2, count = 3, gf = gf_l_l_si)
l_l_si_1_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 2, count = 4, gf = gf_l_l_si)
l_l_si_1_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 2, count = 5, gf = gf_l_l_si)
l_l_si_1_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 2, count = 6, gf = gf_l_l_si)
l_l_si_2_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 2, count = 7, gf = gf_l_l_si)
l_l_si_2_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 2, count = 8, gf = gf_l_l_si)
l_l_si_2_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 2, count = 9, gf = gf_l_l_si)
l_l_si_3_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 2, count = 10, gf = gf_l_l_si)
l_l_si_3_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 2, count = 11, gf = gf_l_l_si)
l_l_si_3_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 2, count = 12, gf = gf_l_l_si)
```

```{r l_l_fc}
l_l_fc_0_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 3, count = 1, gf = gf_l_l_fc)
l_l_fc_0_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 3, count = 2, gf = gf_l_l_fc)
l_l_fc_0_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 3, count = 3, gf = gf_l_l_fc)
l_l_fc_1_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 3, count = 4, gf = gf_l_l_fc)
l_l_fc_1_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 3, count = 5, gf = gf_l_l_fc)
l_l_fc_1_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 3, count = 6, gf = gf_l_l_fc)
l_l_fc_2_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 3, count = 7, gf = gf_l_l_fc)
l_l_fc_2_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 3, count = 8, gf = gf_l_l_fc)
l_l_fc_2_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 3, count = 9, gf = gf_l_l_fc)
l_l_fc_3_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 3, count = 10, gf = gf_l_l_fc)
l_l_fc_3_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 3, count = 11, gf = gf_l_l_fc)
l_l_fc_3_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 3, count = 12, gf = gf_l_l_fc)
```

```{r l_l_ch}
l_l_ch_0_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 4, count = 1, gf = gf_l_l_ch)
l_l_ch_0_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 4, count = 2, gf = gf_l_l_ch)
l_l_ch_0_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 4, count = 3, gf = gf_l_l_ch)
l_l_ch_1_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 4, count = 4, gf = gf_l_l_ch)
l_l_ch_1_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 4, count = 5, gf = gf_l_l_ch)
l_l_ch_1_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 4, count = 6, gf = gf_l_l_ch)
l_l_ch_2_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 4, count = 7, gf = gf_l_l_ch)
l_l_ch_2_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 4, count = 8, gf = gf_l_l_ch)
l_l_ch_2_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 4, count = 9, gf = gf_l_l_ch)
l_l_ch_3_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 4, count = 10, gf = gf_l_l_ch)
l_l_ch_3_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 4, count = 11, gf = gf_l_l_ch)
l_l_ch_3_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 4, count = 12, gf = gf_l_l_ch)

```

```{r l_l_sl}
l_l_sl_0_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 6, count = 1, gf = gf_l_l_sl)
l_l_sl_0_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 6, count = 2, gf = gf_l_l_sl)
l_l_sl_0_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 6, count = 3, gf = gf_l_l_sl)
l_l_sl_1_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 6, count = 4, gf = gf_l_l_sl)
l_l_sl_1_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 6, count = 5, gf = gf_l_l_sl)
l_l_sl_1_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 6, count = 6, gf = gf_l_l_sl)
l_l_sl_2_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 6, count = 7, gf = gf_l_l_sl)
l_l_sl_2_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 6, count = 8, gf = gf_l_l_sl)
l_l_sl_2_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 6, count = 9, gf = gf_l_l_sl)
l_l_sl_3_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 6, count = 10, gf = gf_l_l_sl)
l_l_sl_3_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 6, count = 11, gf = gf_l_l_sl)
l_l_sl_3_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 6, count = 12, gf = gf_l_l_sl)
```

```{r l_l_cu}
l_l_cu_0_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 5, count = 1, gf = gf_l_l_cu)
l_l_cu_0_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 5, count = 2, gf = gf_l_l_cu)
l_l_cu_0_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 5, count = 3, gf = gf_l_l_cu)
l_l_cu_1_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 5, count = 4, gf = gf_l_l_cu)
l_l_cu_1_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 5, count = 5, gf = gf_l_l_cu)
l_l_cu_1_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 5, count = 6, gf = gf_l_l_cu)
l_l_cu_2_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 5, count = 7, gf = gf_l_l_cu)
l_l_cu_2_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 5, count = 8, gf = gf_l_l_cu)
l_l_cu_2_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 5, count = 9, gf = gf_l_l_cu)
l_l_cu_3_0 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 5, count = 10, gf = gf_l_l_cu)
l_l_cu_3_1 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 5, count = 11, gf = gf_l_l_cu)
l_l_cu_3_2 <- location_quality(df = mlbraw2, hand = 3, pitch_type = 5, count = 12, gf = gf_l_l_cu)
```

```{r l_r_ff}
l_r_ff_0_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 1, count = 1, gf = gf_l_r_ff)
l_r_ff_0_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 1, count = 2, gf = gf_l_r_ff)
l_r_ff_0_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 1, count = 3, gf = gf_l_r_ff)
l_r_ff_1_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 1, count = 4, gf = gf_l_r_ff)
l_r_ff_1_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 1, count = 5, gf = gf_l_r_ff)
l_r_ff_1_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 1, count = 6, gf = gf_l_r_ff)
l_r_ff_2_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 1, count = 7, gf = gf_l_r_ff)
l_r_ff_2_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 1, count = 8, gf = gf_l_r_ff)
l_r_ff_2_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 1, count = 9, gf = gf_l_r_ff)
l_r_ff_3_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 1, count = 10, gf = gf_l_r_ff)
l_r_ff_3_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 1, count = 11, gf = gf_l_r_ff)
l_r_ff_3_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 1, count = 12, gf = gf_l_r_ff)
```

```{r l_r_si}
l_r_si_0_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 2, count = 1, gf = gf_l_r_si)
l_r_si_0_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 2, count = 2, gf = gf_l_r_si)
l_r_si_0_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 2, count = 3, gf = gf_l_r_si)
l_r_si_1_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 2, count = 4, gf = gf_l_r_si)
l_r_si_1_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 2, count = 5, gf = gf_l_r_si)
l_r_si_1_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 2, count = 6, gf = gf_l_r_si)
l_r_si_2_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 2, count = 7, gf = gf_l_r_si)
l_r_si_2_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 2, count = 8, gf = gf_l_r_si)
l_r_si_2_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 2, count = 9, gf = gf_l_r_si)
l_r_si_3_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 2, count = 10, gf = gf_l_r_si)
l_r_si_3_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 2, count = 11, gf = gf_l_r_si)
l_r_si_3_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 2, count = 12, gf = gf_l_r_si)
```

```{r l_r_fc}
l_r_fc_0_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 3, count = 1, gf = gf_l_r_fc)
l_r_fc_0_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 3, count = 2, gf = gf_l_r_fc)
l_r_fc_0_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 3, count = 3, gf = gf_l_r_fc)
l_r_fc_1_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 3, count = 4, gf = gf_l_r_fc)
l_r_fc_1_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 3, count = 5, gf = gf_l_r_fc)
l_r_fc_1_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 3, count = 6, gf = gf_l_r_fc)
l_r_fc_2_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 3, count = 7, gf = gf_l_r_fc)
l_r_fc_2_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 3, count = 8, gf = gf_l_r_fc)
l_r_fc_2_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 3, count = 9, gf = gf_l_r_fc)
l_r_fc_3_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 3, count = 10, gf = gf_l_r_fc)
l_r_fc_3_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 3, count = 11, gf = gf_l_r_fc)
l_r_fc_3_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 3, count = 12, gf = gf_l_r_fc)
```

```{r l_r_ch}
l_r_ch_0_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 4, count = 1, gf = gf_l_r_ch)
l_r_ch_0_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 4, count = 2, gf = gf_l_r_ch)
l_r_ch_0_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 4, count = 3, gf = gf_l_r_ch)
l_r_ch_1_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 4, count = 4, gf = gf_l_r_ch)
l_r_ch_1_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 4, count = 5, gf = gf_l_r_ch)
l_r_ch_1_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 4, count = 6, gf = gf_l_r_ch)
l_r_ch_2_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 4, count = 7, gf = gf_l_r_ch)
l_r_ch_2_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 4, count = 8, gf = gf_l_r_ch)
l_r_ch_2_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 4, count = 9, gf = gf_l_r_ch)
l_r_ch_3_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 4, count = 10, gf = gf_l_r_ch)
l_r_ch_3_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 4, count = 11, gf = gf_l_r_ch)
l_r_ch_3_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 4, count = 12, gf = gf_l_r_ch)

```

```{r l_r_sl}
l_r_sl_0_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 6, count = 1, gf = gf_l_r_sl)
l_r_sl_0_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 6, count = 2, gf = gf_l_r_sl)
l_r_sl_0_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 6, count = 3, gf = gf_l_r_sl)
l_r_sl_1_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 6, count = 4, gf = gf_l_r_sl)
l_r_sl_1_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 6, count = 5, gf = gf_l_r_sl)
l_r_sl_1_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 6, count = 6, gf = gf_l_r_sl)
l_r_sl_2_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 6, count = 7, gf = gf_l_r_sl)
l_r_sl_2_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 6, count = 8, gf = gf_l_r_sl)
l_r_sl_2_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 6, count = 9, gf = gf_l_r_sl)
l_r_sl_3_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 6, count = 10, gf = gf_l_r_sl)
l_r_sl_3_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 6, count = 11, gf = gf_l_r_sl)
l_r_sl_3_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 6, count = 12, gf = gf_l_r_sl)
```

```{r l_r_cu}
l_r_cu_0_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 5, count = 1, gf = gf_l_r_cu)
l_r_cu_0_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 5, count = 2, gf = gf_l_r_cu)
l_r_cu_0_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 5, count = 3, gf = gf_l_r_cu)
l_r_cu_1_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 5, count = 4, gf = gf_l_r_cu)
l_r_cu_1_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 5, count = 5, gf = gf_l_r_cu)
l_r_cu_1_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 5, count = 6, gf = gf_l_r_cu)
l_r_cu_2_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 5, count = 7, gf = gf_l_r_cu)
l_r_cu_2_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 5, count = 8, gf = gf_l_r_cu)
l_r_cu_2_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 5, count = 9, gf = gf_l_r_cu)
l_r_cu_3_0 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 5, count = 10, gf = gf_l_r_cu)
l_r_cu_3_1 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 5, count = 11, gf = gf_l_r_cu)
l_r_cu_3_2 <- location_quality(df = mlbraw2, hand = 4, pitch_type = 5, count = 12, gf = gf_l_r_cu)
```

## Create Plots

```{r r_r_ff plots}
plot_r_r_ff_0_0 <- location_quality_plot(r_r_ff_0_0)
plot_r_r_ff_0_1 <- location_quality_plot(r_r_ff_0_1)
plot_r_r_ff_0_2 <- location_quality_plot(r_r_ff_0_2)
plot_r_r_ff_1_0 <- location_quality_plot(r_r_ff_1_0)
plot_r_r_ff_1_1 <- location_quality_plot(r_r_ff_1_1)
plot_r_r_ff_1_2 <- location_quality_plot(r_r_ff_1_2)
plot_r_r_ff_2_0 <- location_quality_plot(r_r_ff_2_0)
plot_r_r_ff_2_1 <- location_quality_plot(r_r_ff_2_1)
plot_r_r_ff_2_2 <- location_quality_plot(r_r_ff_2_2)
plot_r_r_ff_3_0 <- location_quality_plot(r_r_ff_3_0)
plot_r_r_ff_3_1 <- location_quality_plot(r_r_ff_3_1)
plot_r_r_ff_3_2 <- location_quality_plot(r_r_ff_3_2)
```

```{r r_r_si plots}
plot_r_r_si_0_0 <- location_quality_plot(r_r_si_0_0)
plot_r_r_si_0_1 <- location_quality_plot(r_r_si_0_1)
plot_r_r_si_0_2 <- location_quality_plot(r_r_si_0_2)
plot_r_r_si_1_0 <- location_quality_plot(r_r_si_1_0)
plot_r_r_si_1_1 <- location_quality_plot(r_r_si_1_1)
plot_r_r_si_1_2 <- location_quality_plot(r_r_si_1_2)
plot_r_r_si_2_0 <- location_quality_plot(r_r_si_2_0)
plot_r_r_si_2_1 <- location_quality_plot(r_r_si_2_1)
plot_r_r_si_2_2 <- location_quality_plot(r_r_si_2_2)
plot_r_r_si_3_0 <- location_quality_plot(r_r_si_3_0)
plot_r_r_si_3_1 <- location_quality_plot(r_r_si_3_1)
plot_r_r_si_3_2 <- location_quality_plot(r_r_si_3_2)
```

```{r r_r_fc plots}
plot_r_r_fc_0_0 <- location_quality_plot(r_r_fc_0_0)
plot_r_r_fc_0_1 <- location_quality_plot(r_r_fc_0_1)
plot_r_r_fc_0_2 <- location_quality_plot(r_r_fc_0_2)
plot_r_r_fc_1_0 <- location_quality_plot(r_r_fc_1_0)
plot_r_r_fc_1_1 <- location_quality_plot(r_r_fc_1_1)
plot_r_r_fc_1_2 <- location_quality_plot(r_r_fc_1_2)
plot_r_r_fc_2_0 <- location_quality_plot(r_r_fc_2_0)
plot_r_r_fc_2_1 <- location_quality_plot(r_r_fc_2_1)
plot_r_r_fc_2_2 <- location_quality_plot(r_r_fc_2_2)
plot_r_r_fc_3_0 <- location_quality_plot(r_r_fc_3_0)
plot_r_r_fc_3_1 <- location_quality_plot(r_r_fc_3_1)
plot_r_r_fc_3_2 <- location_quality_plot(r_r_fc_3_2)
```

```{r r_r_ch plots}
plot_r_r_ch_0_0 <- location_quality_plot(r_r_ch_0_0)
plot_r_r_ch_0_1 <- location_quality_plot(r_r_ch_0_1)
plot_r_r_ch_0_2 <- location_quality_plot(r_r_ch_0_2)
plot_r_r_ch_1_0 <- location_quality_plot(r_r_ch_1_0)
plot_r_r_ch_1_1 <- location_quality_plot(r_r_ch_1_1)
plot_r_r_ch_1_2 <- location_quality_plot(r_r_ch_1_2)
plot_r_r_ch_2_0 <- location_quality_plot(r_r_ch_2_0)
plot_r_r_ch_2_1 <- location_quality_plot(r_r_ch_2_1)
plot_r_r_ch_2_2 <- location_quality_plot(r_r_ch_2_2)
plot_r_r_ch_3_0 <- location_quality_plot(r_r_ch_3_0)
plot_r_r_ch_3_1 <- location_quality_plot(r_r_ch_3_1)
plot_r_r_ch_3_2 <- location_quality_plot(r_r_ch_3_2)
```

```{r r_r_sl plots}
plot_r_r_sl_0_0 <- location_quality_plot(r_r_sl_0_0)
plot_r_r_sl_0_1 <- location_quality_plot(r_r_sl_0_1)
plot_r_r_sl_0_2 <- location_quality_plot(r_r_sl_0_2)
plot_r_r_sl_1_0 <- location_quality_plot(r_r_sl_1_0)
plot_r_r_sl_1_1 <- location_quality_plot(r_r_sl_1_1)
plot_r_r_sl_1_2 <- location_quality_plot(r_r_sl_1_2)
plot_r_r_sl_2_0 <- location_quality_plot(r_r_sl_2_0)
plot_r_r_sl_2_1 <- location_quality_plot(r_r_sl_2_1)
plot_r_r_sl_2_2 <- location_quality_plot(r_r_sl_2_2)
plot_r_r_sl_3_0 <- location_quality_plot(r_r_sl_3_0)
plot_r_r_sl_3_1 <- location_quality_plot(r_r_sl_3_1)
plot_r_r_sl_3_2 <- location_quality_plot(r_r_sl_3_2)
```

```{r r_r_cu plots}
plot_r_r_cu_0_0 <- location_quality_plot(r_r_cu_0_0)
plot_r_r_cu_0_1 <- location_quality_plot(r_r_cu_0_1)
plot_r_r_cu_0_2 <- location_quality_plot(r_r_cu_0_2)
plot_r_r_cu_1_0 <- location_quality_plot(r_r_cu_1_0)
plot_r_r_cu_1_1 <- location_quality_plot(r_r_cu_1_1)
plot_r_r_cu_1_2 <- location_quality_plot(r_r_cu_1_2)
plot_r_r_cu_2_0 <- location_quality_plot(r_r_cu_2_0)
plot_r_r_cu_2_1 <- location_quality_plot(r_r_cu_2_1)
plot_r_r_cu_2_2 <- location_quality_plot(r_r_cu_2_2)
plot_r_r_cu_3_0 <- location_quality_plot(r_r_cu_3_0)
plot_r_r_cu_3_1 <- location_quality_plot(r_r_cu_3_1)
plot_r_r_cu_3_2 <- location_quality_plot(r_r_cu_3_2)
```

```{r r_l_ff plots}
plot_r_l_ff_0_0 <- location_quality_plot(r_l_ff_0_0)
plot_r_l_ff_0_1 <- location_quality_plot(r_l_ff_0_1)
plot_r_l_ff_0_2 <- location_quality_plot(r_l_ff_0_2)
plot_r_l_ff_1_0 <- location_quality_plot(r_l_ff_1_0)
plot_r_l_ff_1_1 <- location_quality_plot(r_l_ff_1_1)
plot_r_l_ff_1_2 <- location_quality_plot(r_l_ff_1_2)
plot_r_l_ff_2_0 <- location_quality_plot(r_l_ff_2_0)
plot_r_l_ff_2_1 <- location_quality_plot(r_l_ff_2_1)
plot_r_l_ff_2_2 <- location_quality_plot(r_l_ff_2_2)
plot_r_l_ff_3_0 <- location_quality_plot(r_l_ff_3_0)
plot_r_l_ff_3_1 <- location_quality_plot(r_l_ff_3_1)
plot_r_l_ff_3_2 <- location_quality_plot(r_l_ff_3_2)
```

```{r r_l_si plots}
plot_r_l_si_0_0 <- location_quality_plot(r_l_si_0_0)
plot_r_l_si_0_1 <- location_quality_plot(r_l_si_0_1)
plot_r_l_si_0_2 <- location_quality_plot(r_l_si_0_2)
plot_r_l_si_1_0 <- location_quality_plot(r_l_si_1_0)
plot_r_l_si_1_1 <- location_quality_plot(r_l_si_1_1)
plot_r_l_si_1_2 <- location_quality_plot(r_l_si_1_2)
plot_r_l_si_2_0 <- location_quality_plot(r_l_si_2_0)
plot_r_l_si_2_1 <- location_quality_plot(r_l_si_2_1)
plot_r_l_si_2_2 <- location_quality_plot(r_l_si_2_2)
plot_r_l_si_3_0 <- location_quality_plot(r_l_si_3_0)
plot_r_l_si_3_1 <- location_quality_plot(r_l_si_3_1)
plot_r_l_si_3_2 <- location_quality_plot(r_l_si_3_2)
```

```{r r_l_fc plots}
plot_r_l_fc_0_0 <- location_quality_plot(r_l_fc_0_0)
plot_r_l_fc_0_1 <- location_quality_plot(r_l_fc_0_1)
plot_r_l_fc_0_2 <- location_quality_plot(r_l_fc_0_2)
plot_r_l_fc_1_0 <- location_quality_plot(r_l_fc_1_0)
plot_r_l_fc_1_1 <- location_quality_plot(r_l_fc_1_1)
plot_r_l_fc_1_2 <- location_quality_plot(r_l_fc_1_2)
plot_r_l_fc_2_0 <- location_quality_plot(r_l_fc_2_0)
plot_r_l_fc_2_1 <- location_quality_plot(r_l_fc_2_1)
plot_r_l_fc_2_2 <- location_quality_plot(r_l_fc_2_2)
plot_r_l_fc_3_0 <- location_quality_plot(r_l_fc_3_0)
plot_r_l_fc_3_1 <- location_quality_plot(r_l_fc_3_1)
plot_r_l_fc_3_2 <- location_quality_plot(r_l_fc_3_2)
```

```{r r_l_ch plots}
plot_r_l_ch_0_0 <- location_quality_plot(r_l_ch_0_0)
plot_r_l_ch_0_1 <- location_quality_plot(r_l_ch_0_1)
plot_r_l_ch_0_2 <- location_quality_plot(r_l_ch_0_2)
plot_r_l_ch_1_0 <- location_quality_plot(r_l_ch_1_0)
plot_r_l_ch_1_1 <- location_quality_plot(r_l_ch_1_1)
plot_r_l_ch_1_2 <- location_quality_plot(r_l_ch_1_2)
plot_r_l_ch_2_0 <- location_quality_plot(r_l_ch_2_0)
plot_r_l_ch_2_1 <- location_quality_plot(r_l_ch_2_1)
plot_r_l_ch_2_2 <- location_quality_plot(r_l_ch_2_2)
plot_r_l_ch_3_0 <- location_quality_plot(r_l_ch_3_0)
plot_r_l_ch_3_1 <- location_quality_plot(r_l_ch_3_1)
plot_r_l_ch_3_2 <- location_quality_plot(r_l_ch_3_2)
```

```{r r_l_sl plots}
plot_r_l_sl_0_0 <- location_quality_plot(r_l_sl_0_0)
plot_r_l_sl_0_1 <- location_quality_plot(r_l_sl_0_1)
plot_r_l_sl_0_2 <- location_quality_plot(r_l_sl_0_2)
plot_r_l_sl_1_0 <- location_quality_plot(r_l_sl_1_0)
plot_r_l_sl_1_1 <- location_quality_plot(r_l_sl_1_1)
plot_r_l_sl_1_2 <- location_quality_plot(r_l_sl_1_2)
plot_r_l_sl_2_0 <- location_quality_plot(r_l_sl_2_0)
plot_r_l_sl_2_1 <- location_quality_plot(r_l_sl_2_1)
plot_r_l_sl_2_2 <- location_quality_plot(r_l_sl_2_2)
plot_r_l_sl_3_0 <- location_quality_plot(r_l_sl_3_0)
plot_r_l_sl_3_1 <- location_quality_plot(r_l_sl_3_1)
plot_r_l_sl_3_2 <- location_quality_plot(r_l_sl_3_2)
```

```{r r_l_cu plots}
plot_r_l_cu_0_0 <- location_quality_plot(r_l_cu_0_0)
plot_r_l_cu_0_1 <- location_quality_plot(r_l_cu_0_1)
plot_r_l_cu_0_2 <- location_quality_plot(r_l_cu_0_2)
plot_r_l_cu_1_0 <- location_quality_plot(r_l_cu_1_0)
plot_r_l_cu_1_1 <- location_quality_plot(r_l_cu_1_1)
plot_r_l_cu_1_2 <- location_quality_plot(r_l_cu_1_2)
plot_r_l_cu_2_0 <- location_quality_plot(r_l_cu_2_0)
plot_r_l_cu_2_1 <- location_quality_plot(r_l_cu_2_1)
plot_r_l_cu_2_2 <- location_quality_plot(r_l_cu_2_2)
plot_r_l_cu_3_0 <- location_quality_plot(r_l_cu_3_0)
plot_r_l_cu_3_1 <- location_quality_plot(r_l_cu_3_1)
plot_r_l_cu_3_2 <- location_quality_plot(r_l_cu_3_2)
```

```{r l_l_ff plots}
plot_l_l_ff_0_0 <- location_quality_plot(l_l_ff_0_0)
plot_l_l_ff_0_1 <- location_quality_plot(l_l_ff_0_1)
plot_l_l_ff_0_2 <- location_quality_plot(l_l_ff_0_2)
plot_l_l_ff_1_0 <- location_quality_plot(l_l_ff_1_0)
plot_l_l_ff_1_1 <- location_quality_plot(l_l_ff_1_1)
plot_l_l_ff_1_2 <- location_quality_plot(l_l_ff_1_2)
plot_l_l_ff_2_0 <- location_quality_plot(l_l_ff_2_0)
plot_l_l_ff_2_1 <- location_quality_plot(l_l_ff_2_1)
plot_l_l_ff_2_2 <- location_quality_plot(l_l_ff_2_2)
plot_l_l_ff_3_0 <- location_quality_plot(l_l_ff_3_0)
plot_l_l_ff_3_1 <- location_quality_plot(l_l_ff_3_1)
plot_l_l_ff_3_2 <- location_quality_plot(l_l_ff_3_2)
```

```{r l_l_si plots}
plot_l_l_si_0_0 <- location_quality_plot(l_l_si_0_0)
plot_l_l_si_0_1 <- location_quality_plot(l_l_si_0_1)
plot_l_l_si_0_2 <- location_quality_plot(l_l_si_0_2)
plot_l_l_si_1_0 <- location_quality_plot(l_l_si_1_0)
plot_l_l_si_1_1 <- location_quality_plot(l_l_si_1_1)
plot_l_l_si_1_2 <- location_quality_plot(l_l_si_1_2)
plot_l_l_si_2_0 <- location_quality_plot(l_l_si_2_0)
plot_l_l_si_2_1 <- location_quality_plot(l_l_si_2_1)
plot_l_l_si_2_2 <- location_quality_plot(l_l_si_2_2)
plot_l_l_si_3_0 <- location_quality_plot(l_l_si_3_0)
plot_l_l_si_3_1 <- location_quality_plot(l_l_si_3_1)
plot_l_l_si_3_2 <- location_quality_plot(l_l_si_3_2)
```

```{r l_l_fc plots}
plot_l_l_fc_0_0 <- location_quality_plot(l_l_fc_0_0)
plot_l_l_fc_0_1 <- location_quality_plot(l_l_fc_0_1)
plot_l_l_fc_0_2 <- location_quality_plot(l_l_fc_0_2)
plot_l_l_fc_1_0 <- location_quality_plot(l_l_fc_1_0)
plot_l_l_fc_1_1 <- location_quality_plot(l_l_fc_1_1)
plot_l_l_fc_1_2 <- location_quality_plot(l_l_fc_1_2)
plot_l_l_fc_2_0 <- location_quality_plot(l_l_fc_2_0)
plot_l_l_fc_2_1 <- location_quality_plot(l_l_fc_2_1)
plot_l_l_fc_2_2 <- location_quality_plot(l_l_fc_2_2)
plot_l_l_fc_3_0 <- location_quality_plot(l_l_fc_3_0)
plot_l_l_fc_3_1 <- location_quality_plot(l_l_fc_3_1)
plot_l_l_fc_3_2 <- location_quality_plot(l_l_fc_3_2)
```

```{r l_l_ch plots}
plot_l_l_ch_0_0 <- location_quality_plot(l_l_ch_0_0)
plot_l_l_ch_0_1 <- location_quality_plot(l_l_ch_0_1)
plot_l_l_ch_0_2 <- location_quality_plot(l_l_ch_0_2)
plot_l_l_ch_1_0 <- location_quality_plot(l_l_ch_1_0)
plot_l_l_ch_1_1 <- location_quality_plot(l_l_ch_1_1)
plot_l_l_ch_1_2 <- location_quality_plot(l_l_ch_1_2)
plot_l_l_ch_2_0 <- location_quality_plot(l_l_ch_2_0)
plot_l_l_ch_2_1 <- location_quality_plot(l_l_ch_2_1)
plot_l_l_ch_2_2 <- location_quality_plot(l_l_ch_2_2)
plot_l_l_ch_3_0 <- location_quality_plot(l_l_ch_3_0)
plot_l_l_ch_3_1 <- location_quality_plot(l_l_ch_3_1)
plot_l_l_ch_3_2 <- location_quality_plot(l_l_ch_3_2)
```

```{r l_l_sl plots}
plot_l_l_sl_0_0 <- location_quality_plot(l_l_sl_0_0)
plot_l_l_sl_0_1 <- location_quality_plot(l_l_sl_0_1)
plot_l_l_sl_0_2 <- location_quality_plot(l_l_sl_0_2)
plot_l_l_sl_1_0 <- location_quality_plot(l_l_sl_1_0)
plot_l_l_sl_1_1 <- location_quality_plot(l_l_sl_1_1)
plot_l_l_sl_1_2 <- location_quality_plot(l_l_sl_1_2)
plot_l_l_sl_2_0 <- location_quality_plot(l_l_sl_2_0)
plot_l_l_sl_2_1 <- location_quality_plot(l_l_sl_2_1)
plot_l_l_sl_2_2 <- location_quality_plot(l_l_sl_2_2)
plot_l_l_sl_3_0 <- location_quality_plot(l_l_sl_3_0)
plot_l_l_sl_3_1 <- location_quality_plot(l_l_sl_3_1)
plot_l_l_sl_3_2 <- location_quality_plot(l_l_sl_3_2)
```

```{r l_l_cu plots}
plot_l_l_cu_0_0 <- location_quality_plot(l_l_cu_0_0)
plot_l_l_cu_0_1 <- location_quality_plot(l_l_cu_0_1)
plot_l_l_cu_0_2 <- location_quality_plot(l_l_cu_0_2)
plot_l_l_cu_1_0 <- location_quality_plot(l_l_cu_1_0)
plot_l_l_cu_1_1 <- location_quality_plot(l_l_cu_1_1)
plot_l_l_cu_1_2 <- location_quality_plot(l_l_cu_1_2)
plot_l_l_cu_2_0 <- location_quality_plot(l_l_cu_2_0)
plot_l_l_cu_2_1 <- location_quality_plot(l_l_cu_2_1)
plot_l_l_cu_2_2 <- location_quality_plot(l_l_cu_2_2)
plot_l_l_cu_3_0 <- location_quality_plot(l_l_cu_3_0)
plot_l_l_cu_3_1 <- location_quality_plot(l_l_cu_3_1)
plot_l_l_cu_3_2 <- location_quality_plot(l_l_cu_3_2)
```

```{r l_r_ff plots}
plot_l_r_ff_0_0 <- location_quality_plot(l_r_ff_0_0)
plot_l_r_ff_0_1 <- location_quality_plot(l_r_ff_0_1)
plot_l_r_ff_0_2 <- location_quality_plot(l_r_ff_0_2)
plot_l_r_ff_1_0 <- location_quality_plot(l_r_ff_1_0)
plot_l_r_ff_1_1 <- location_quality_plot(l_r_ff_1_1)
plot_l_r_ff_1_2 <- location_quality_plot(l_r_ff_1_2)
plot_l_r_ff_2_0 <- location_quality_plot(l_r_ff_2_0)
plot_l_r_ff_2_1 <- location_quality_plot(l_r_ff_2_1)
plot_l_r_ff_2_2 <- location_quality_plot(l_r_ff_2_2)
plot_l_r_ff_3_0 <- location_quality_plot(l_r_ff_3_0)
plot_l_r_ff_3_1 <- location_quality_plot(l_r_ff_3_1)
plot_l_r_ff_3_2 <- location_quality_plot(l_r_ff_3_2)
```

```{r l_r_si plots}
plot_l_r_si_0_0 <- location_quality_plot(l_r_si_0_0)
plot_l_r_si_0_1 <- location_quality_plot(l_r_si_0_1)
plot_l_r_si_0_2 <- location_quality_plot(l_r_si_0_2)
plot_l_r_si_1_0 <- location_quality_plot(l_r_si_1_0)
plot_l_r_si_1_1 <- location_quality_plot(l_r_si_1_1)
plot_l_r_si_1_2 <- location_quality_plot(l_r_si_1_2)
plot_l_r_si_2_0 <- location_quality_plot(l_r_si_2_0)
plot_l_r_si_2_1 <- location_quality_plot(l_r_si_2_1)
plot_l_r_si_2_2 <- location_quality_plot(l_r_si_2_2)
plot_l_r_si_3_0 <- location_quality_plot(l_r_si_3_0)
plot_l_r_si_3_1 <- location_quality_plot(l_r_si_3_1)
plot_l_r_si_3_2 <- location_quality_plot(l_r_si_3_2)
```

```{r l_r_fc plots}
plot_l_r_fc_0_0 <- location_quality_plot(l_r_fc_0_0)
plot_l_r_fc_0_1 <- location_quality_plot(l_r_fc_0_1)
plot_l_r_fc_0_2 <- location_quality_plot(l_r_fc_0_2)
plot_l_r_fc_1_0 <- location_quality_plot(l_r_fc_1_0)
plot_l_r_fc_1_1 <- location_quality_plot(l_r_fc_1_1)
plot_l_r_fc_1_2 <- location_quality_plot(l_r_fc_1_2)
plot_l_r_fc_2_0 <- location_quality_plot(l_r_fc_2_0)
plot_l_r_fc_2_1 <- location_quality_plot(l_r_fc_2_1)
plot_l_r_fc_2_2 <- location_quality_plot(l_r_fc_2_2)
plot_l_r_fc_3_0 <- location_quality_plot(l_r_fc_3_0)
plot_l_r_fc_3_1 <- location_quality_plot(l_r_fc_3_1)
plot_l_r_fc_3_2 <- location_quality_plot(l_r_fc_3_2)
```

```{r l_r_ch plots}
plot_l_r_ch_0_0 <- location_quality_plot(l_r_ch_0_0)
plot_l_r_ch_0_1 <- location_quality_plot(l_r_ch_0_1)
plot_l_r_ch_0_2 <- location_quality_plot(l_r_ch_0_2)
plot_l_r_ch_1_0 <- location_quality_plot(l_r_ch_1_0)
plot_l_r_ch_1_1 <- location_quality_plot(l_r_ch_1_1)
plot_l_r_ch_1_2 <- location_quality_plot(l_r_ch_1_2)
plot_l_r_ch_2_0 <- location_quality_plot(l_r_ch_2_0)
plot_l_r_ch_2_1 <- location_quality_plot(l_r_ch_2_1)
plot_l_r_ch_2_2 <- location_quality_plot(l_r_ch_2_2)
plot_l_r_ch_3_0 <- location_quality_plot(l_r_ch_3_0)
plot_l_r_ch_3_1 <- location_quality_plot(l_r_ch_3_1)
plot_l_r_ch_3_2 <- location_quality_plot(l_r_ch_3_2)
```

```{r l_r_sl plots}
plot_l_r_sl_0_0 <- location_quality_plot(l_r_sl_0_0)
plot_l_r_sl_0_1 <- location_quality_plot(l_r_sl_0_1)
plot_l_r_sl_0_2 <- location_quality_plot(l_r_sl_0_2)
plot_l_r_sl_1_0 <- location_quality_plot(l_r_sl_1_0)
plot_l_r_sl_1_1 <- location_quality_plot(l_r_sl_1_1)
plot_l_r_sl_1_2 <- location_quality_plot(l_r_sl_1_2)
plot_l_r_sl_2_0 <- location_quality_plot(l_r_sl_2_0)
plot_l_r_sl_2_1 <- location_quality_plot(l_r_sl_2_1)
plot_l_r_sl_2_2 <- location_quality_plot(l_r_sl_2_2)
plot_l_r_sl_3_0 <- location_quality_plot(l_r_sl_3_0)
plot_l_r_sl_3_1 <- location_quality_plot(l_r_sl_3_1)
plot_l_r_sl_3_2 <- location_quality_plot(l_r_sl_3_2)
```

```{r l_r_cu plots}
plot_l_r_cu_0_0 <- location_quality_plot(l_r_cu_0_0)
plot_l_r_cu_0_1 <- location_quality_plot(l_r_cu_0_1)
plot_l_r_cu_0_2 <- location_quality_plot(l_r_cu_0_2)
plot_l_r_cu_1_0 <- location_quality_plot(l_r_cu_1_0)
plot_l_r_cu_1_1 <- location_quality_plot(l_r_cu_1_1)
plot_l_r_cu_1_2 <- location_quality_plot(l_r_cu_1_2)
plot_l_r_cu_2_0 <- location_quality_plot(l_r_cu_2_0)
plot_l_r_cu_2_1 <- location_quality_plot(l_r_cu_2_1)
plot_l_r_cu_2_2 <- location_quality_plot(l_r_cu_2_2)
plot_l_r_cu_3_0 <- location_quality_plot(l_r_cu_3_0)
plot_l_r_cu_3_1 <- location_quality_plot(l_r_cu_3_1)
plot_l_r_cu_3_2 <- location_quality_plot(l_r_cu_3_2)
```

```{r r_r_ff arrange}
r_r_ff <- ggarrange(plot_r_r_ff_0_0,plot_r_r_ff_1_0,plot_r_r_ff_2_0,plot_r_r_ff_3_0,
          plot_r_r_ff_0_1,plot_r_r_ff_1_1,plot_r_r_ff_2_1,plot_r_r_ff_3_1,
          plot_r_r_ff_0_2,plot_r_r_ff_1_2,plot_r_r_ff_2_2,plot_r_r_ff_3_2,
          nrow=3, ncol=4)
```

```{r r_r_si arrange}
r_r_si <- ggarrange(plot_r_r_si_0_0,plot_r_r_si_1_0,plot_r_r_si_2_0,plot_r_r_si_3_0,
          plot_r_r_si_0_1,plot_r_r_si_1_1,plot_r_r_si_2_1,plot_r_r_si_3_1,
          plot_r_r_si_0_2,plot_r_r_si_1_2,plot_r_r_si_2_2,plot_r_r_si_3_2,
          nrow=3, ncol=4)
```

```{r r_r_fc arrange}
r_r_fc <- ggarrange(plot_r_r_fc_0_0,plot_r_r_fc_1_0,plot_r_r_fc_2_0,plot_r_r_fc_3_0,
          plot_r_r_fc_0_1,plot_r_r_fc_1_1,plot_r_r_fc_2_1,plot_r_r_fc_3_1,
          plot_r_r_fc_0_2,plot_r_r_fc_1_2,plot_r_r_fc_2_2,plot_r_r_fc_3_2,
          nrow=3, ncol=4)
```

```{r r_r_ch arrange}
r_r_ch <- ggarrange(plot_r_r_ch_0_0,plot_r_r_ch_1_0,plot_r_r_ch_2_0,plot_r_r_ch_3_0,
          plot_r_r_ch_0_1,plot_r_r_ch_1_1,plot_r_r_ch_2_1,plot_r_r_ch_3_1,
          plot_r_r_ch_0_2,plot_r_r_ch_1_2,plot_r_r_ch_2_2,plot_r_r_ch_3_2,
          nrow=3, ncol=4)
```

```{r r_r_cu arrange}
r_r_cu <- ggarrange(plot_r_r_cu_0_0,plot_r_r_cu_1_0,plot_r_r_cu_2_0,plot_r_r_cu_3_0,
          plot_r_r_cu_0_1,plot_r_r_cu_1_1,plot_r_r_cu_2_1,plot_r_r_cu_3_1,
          plot_r_r_cu_0_2,plot_r_r_cu_1_2,plot_r_r_cu_2_2,plot_r_r_cu_3_2,
          nrow=3, ncol=4)
```

```{r r_r_sl arrange}
r_r_sl <- ggarrange(plot_r_r_sl_0_0,plot_r_r_sl_1_0,plot_r_r_sl_2_0,plot_r_r_sl_3_0,
          plot_r_r_sl_0_1,plot_r_r_sl_1_1,plot_r_r_sl_2_1,plot_r_r_sl_3_1,
          plot_r_r_sl_0_2,plot_r_r_sl_1_2,plot_r_r_sl_2_2,plot_r_r_sl_3_2,
          nrow=3, ncol=4)
```

```{r r_l_ff arrange}
r_l_ff <- ggarrange(plot_r_l_ff_0_0,plot_r_l_ff_1_0,plot_r_l_ff_2_0,plot_r_l_ff_3_0,
          plot_r_l_ff_0_1,plot_r_l_ff_1_1,plot_r_l_ff_2_1,plot_r_l_ff_3_1,
          plot_r_l_ff_0_2,plot_r_l_ff_1_2,plot_r_l_ff_2_2,plot_r_l_ff_3_2,
          nrow=3, ncol=4)
```

```{r r_l_si arrange}
r_l_si <- ggarrange(plot_r_l_si_0_0,plot_r_l_si_1_0,plot_r_l_si_2_0,plot_r_l_si_3_0,
          plot_r_l_si_0_1,plot_r_l_si_1_1,plot_r_l_si_2_1,plot_r_l_si_3_1,
          plot_r_l_si_0_2,plot_r_l_si_1_2,plot_r_l_si_2_2,plot_r_l_si_3_2,
          nrow=3, ncol=4)
```

```{r r_l_fc arrange}
r_l_fc <- ggarrange(plot_r_l_fc_0_0,plot_r_l_fc_1_0,plot_r_l_fc_2_0,plot_r_l_fc_3_0,
          plot_r_l_fc_0_1,plot_r_l_fc_1_1,plot_r_l_fc_2_1,plot_r_l_fc_3_1,
          plot_r_l_fc_0_2,plot_r_l_fc_1_2,plot_r_l_fc_2_2,plot_r_l_fc_3_2,
          nrow=3, ncol=4)
```

```{r r_l_ch arrange}
r_l_ch <- ggarrange(plot_r_l_ch_0_0,plot_r_l_ch_1_0,plot_r_l_ch_2_0,plot_r_l_ch_3_0,
          plot_r_l_ch_0_1,plot_r_l_ch_1_1,plot_r_l_ch_2_1,plot_r_l_ch_3_1,
          plot_r_l_ch_0_2,plot_r_l_ch_1_2,plot_r_l_ch_2_2,plot_r_l_ch_3_2,
          nrow=3, ncol=4)
```

```{r r_l_cu arrange}
r_l_cu <- ggarrange(plot_r_l_cu_0_0,plot_r_l_cu_1_0,plot_r_l_cu_2_0,plot_r_l_cu_3_0,
          plot_r_l_cu_0_1,plot_r_l_cu_1_1,plot_r_l_cu_2_1,plot_r_l_cu_3_1,
          plot_r_l_cu_0_2,plot_r_l_cu_1_2,plot_r_l_cu_2_2,plot_r_l_cu_3_2,
          nrow=3, ncol=4)
```

```{r r_l_sl arrange}
r_l_sl <- ggarrange(plot_r_l_sl_0_0,plot_r_l_sl_1_0,plot_r_l_sl_2_0,plot_r_l_sl_3_0,
          plot_r_l_sl_0_1,plot_r_l_sl_1_1,plot_r_l_sl_2_1,plot_r_l_sl_3_1,
          plot_r_l_sl_0_2,plot_r_l_sl_1_2,plot_r_l_sl_2_2,plot_r_l_sl_3_2,
          nrow=3, ncol=4)
```

```{r l_l_ff arrange}
l_l_ff <- ggarrange(plot_l_l_ff_0_0,plot_l_l_ff_1_0,plot_l_l_ff_2_0,plot_l_l_ff_3_0,
          plot_l_l_ff_0_1,plot_l_l_ff_1_1,plot_l_l_ff_2_1,plot_l_l_ff_3_1,
          plot_l_l_ff_0_2,plot_l_l_ff_1_2,plot_l_l_ff_2_2,plot_l_l_ff_3_2,
          nrow=3, ncol=4)
```

```{r l_l_si arrange}
l_l_si <- ggarrange(plot_l_l_si_0_0,plot_l_l_si_1_0,plot_l_l_si_2_0,plot_l_l_si_3_0,
          plot_l_l_si_0_1,plot_l_l_si_1_1,plot_l_l_si_2_1,plot_l_l_si_3_1,
          plot_l_l_si_0_2,plot_l_l_si_1_2,plot_l_l_si_2_2,plot_l_l_si_3_2,
          nrow=3, ncol=4)
```

```{r l_l_fc arrange}
l_l_fc <- ggarrange(plot_l_l_fc_0_0,plot_l_l_fc_1_0,plot_l_l_fc_2_0,plot_l_l_fc_3_0,
          plot_l_l_fc_0_1,plot_l_l_fc_1_1,plot_l_l_fc_2_1,plot_l_l_fc_3_1,
          plot_l_l_fc_0_2,plot_l_l_fc_1_2,plot_l_l_fc_2_2,plot_l_l_fc_3_2,
          nrow=3, ncol=4)
```

```{r l_l_ch arrange}
l_l_ch <- ggarrange(plot_l_l_ch_0_0,plot_l_l_ch_1_0,plot_l_l_ch_2_0,plot_l_l_ch_3_0,
          plot_l_l_ch_0_1,plot_l_l_ch_1_1,plot_l_l_ch_2_1,plot_l_l_ch_3_1,
          plot_l_l_ch_0_2,plot_l_l_ch_1_2,plot_l_l_ch_2_2,plot_l_l_ch_3_2,
          nrow=3, ncol=4)
```

```{r l_l_cu arrange}
l_l_cu <- ggarrange(plot_l_l_cu_0_0,plot_l_l_cu_1_0,plot_l_l_cu_2_0,plot_l_l_cu_3_0,
          plot_l_l_cu_0_1,plot_l_l_cu_1_1,plot_l_l_cu_2_1,plot_l_l_cu_3_1,
          plot_l_l_cu_0_2,plot_l_l_cu_1_2,plot_l_l_cu_2_2,plot_l_l_cu_3_2,
          nrow=3, ncol=4)
```

```{r l_l_sl arrange}
l_l_sl <- ggarrange(plot_l_l_sl_0_0,plot_l_l_sl_1_0,plot_l_l_sl_2_0,plot_l_l_sl_3_0,
          plot_l_l_sl_0_1,plot_l_l_sl_1_1,plot_l_l_sl_2_1,plot_l_l_sl_3_1,
          plot_l_l_sl_0_2,plot_l_l_sl_1_2,plot_l_l_sl_2_2,plot_l_l_sl_3_2,
          nrow=3, ncol=4)
```

```{r l_r_ff arrange}
l_r_ff <- ggarrange(plot_l_r_ff_0_0,plot_l_r_ff_1_0,plot_l_r_ff_2_0,plot_l_r_ff_3_0,
          plot_l_r_ff_0_1,plot_l_r_ff_1_1,plot_l_r_ff_2_1,plot_l_r_ff_3_1,
          plot_l_r_ff_0_2,plot_l_r_ff_1_2,plot_l_r_ff_2_2,plot_l_r_ff_3_2,
          nrow=3, ncol=4)
```

```{r l_r_si arrange}
l_r_si <- ggarrange(plot_l_r_si_0_0,plot_l_r_si_1_0,plot_l_r_si_2_0,plot_l_r_si_3_0,
          plot_l_r_si_0_1,plot_l_r_si_1_1,plot_l_r_si_2_1,plot_l_r_si_3_1,
          plot_l_r_si_0_2,plot_l_r_si_1_2,plot_l_r_si_2_2,plot_l_r_si_3_2,
          nrow=3, ncol=4)
```

```{r l_r_fc arrange}
l_r_fc <- ggarrange(plot_l_r_fc_0_0,plot_l_r_fc_1_0,plot_l_r_fc_2_0,plot_l_r_fc_3_0,
          plot_l_r_fc_0_1,plot_l_r_fc_1_1,plot_l_r_fc_2_1,plot_l_r_fc_3_1,
          plot_l_r_fc_0_2,plot_l_r_fc_1_2,plot_l_r_fc_2_2,plot_l_r_fc_3_2,
          nrow=3, ncol=4)
```

```{r l_r_ch arrange}
l_r_ch <- ggarrange(plot_l_r_ch_0_0,plot_l_r_ch_1_0,plot_l_r_ch_2_0,plot_l_r_ch_3_0,
          plot_l_r_ch_0_1,plot_l_r_ch_1_1,plot_l_r_ch_2_1,plot_l_r_ch_3_1,
          plot_l_r_ch_0_2,plot_l_r_ch_1_2,plot_l_r_ch_2_2,plot_l_r_ch_3_2,
          nrow=3, ncol=4)
```

```{r l_r_cu arrange}
l_r_cu <- ggarrange(plot_l_r_cu_0_0,plot_l_r_cu_1_0,plot_l_r_cu_2_0,plot_l_r_cu_3_0,
          plot_l_r_cu_0_1,plot_l_r_cu_1_1,plot_l_r_cu_2_1,plot_l_r_cu_3_1,
          plot_l_r_cu_0_2,plot_l_r_cu_1_2,plot_l_r_cu_2_2,plot_l_r_cu_3_2,
          nrow=3, ncol=4)
```

```{r l_r_sl arrange}
l_r_sl <- ggarrange(plot_l_r_sl_0_0,plot_l_r_sl_1_0,plot_l_r_sl_2_0,plot_l_r_sl_3_0,
          plot_l_r_sl_0_1,plot_l_r_sl_1_1,plot_l_r_sl_2_1,plot_l_r_sl_3_1,
          plot_l_r_sl_0_2,plot_l_r_sl_1_2,plot_l_r_sl_2_2,plot_l_r_sl_3_2,
          nrow=3, ncol=4)
```
