# Applying Results to 2023 Season

Now we have a compiled pitch quality data frame that can be joined to a season's worth of data. So any given pitch from 2023 will have a corresponding pitch location value. However, outlier pitches falling outside the 99% region will not have a corresponding pitch value. For the time being, these pitches are removed from the analysis going forward.

Here, I'll load 2023 season data back in and do some cleaning before joining the pitch quality lookup data frame to it. 

## Cleaning 2023 Dataset

```{r cleaning 2023}
mlbraw2023 <- read.csv("/Users/dougrose/Desktop/location/raw_statcast/mlbraw2023.csv")
mlbraw2023$game_date <- as.Date(mlbraw2023$game_date, format="%m/%d/%y")

mlbraw2023 <- mlbraw2023 %>%
  mutate(events = if_else(is.na(events) | events == "", type, events)) %>%
  mutate(events = if_else(events == "B", "ball", 
                          if_else(events == "S", "strike", events))) %>%
  mutate(count = paste(balls, strikes, sep="-")) %>%
  mutate(hand = paste(p_throws, stand, sep = "v")) %>%
select(player_name, pitch_type, pitch_name, count, hand, plate_x, plate_z)

mlbraw2023 <- mlbraw2023 %>% 
  filter(pitch_type %in% c("FF","SI","FC","FS","CH","CU",
                           "CS","KC","SV","SL","ST"))

mlbraw2023 <- mlbraw2023 %>%
  mutate(pitch_type2 = if_else(pitch_type %in% c("CU","CS","KC","SV"), "CU",
                              if_else(pitch_type %in% c("CH","FS"), "CH",
                                      if_else(pitch_type %in% c("SL","ST"), "SL", 
                                              pitch_type))))

mlbraw2023 <- mlbraw2023 %>%
  inner_join(huge_lookup, 
             join_by(hand==hand, pitch_type2==pitch_type, count==count, plate_x==x, plate_z==y))

mlbraw2023 <- mlbraw2023 %>%
  mutate(pitch_type = if_else(pitch_type %in% c("CU","CS","KC","SV"), "CU", pitch_type)) %>%
  select(-pitch_type2)

mlbraw2023 <- mlbraw2023 %>% 
  mutate(pitch_name = if_else(
    pitch_name == "4-Seam Fastball", "Fastball",
    if_else(pitch_name %in% c("Curveball","Slow Curve","Knuckle Curve", "Slurve"), "Curveball",
            if_else(pitch_name == "Split-Finger", "Splitter", pitch_name))))
```

## Distribution of Location Quality by Pitch Type

I'll briefly profile the resulting pitch quality metric. Accounting for all pitches in 2023 with a corresponding pitch location quality number, here is the distribution of values based on pitch type. Across all 6 pitch type levels, a similar distribution pattern emerges. We see the highest peak of around 0.8 across all pitch types followed by a lower peak around 0.25. 4-Seam Fastballs, Sinkers, and Cutters have better overall pitch location values compared to Changeups. Changeups have a more even distribution of values from 0 to 1. Meaning we would expect pitchers throwing a high rate of Changeups in 2023 to generally score lower than other pitchers.

```{r distribution of location quality by pitch type, fig.height = 8, fig.width = 8, fig.align = "left"}
ff <- mlbraw2023 %>%
  filter(pitch_type == "FF") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.025) +
  ylim(0,0.06)+
  ylab("4-seam fastballs")+
  theme_classic()
si <- mlbraw2023 %>%
  filter(pitch_type == "SI") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.025) +
  ylim(0,0.06)+
  ylab("sinkers")+
  theme_classic()
fc <- mlbraw2023 %>%
  filter(pitch_type == "FC") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.025) +
  ylim(0,0.06)+
  ylab("cutters")+
  theme_classic()
ch <- mlbraw2023 %>%
  filter(pitch_type == "CH") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.025) +
  ylim(0,0.06)+
  ylab("changeups")+
  theme_classic()
cu <- mlbraw2023 %>%
  filter(pitch_type == "CU") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.025) +
  ylim(0,0.06)+
  ylab("curveballs")+
  theme_classic()
sl <- mlbraw2023 %>%
  filter(pitch_type == "SL") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.025) +
  ylim(0,0.06)+
  ylab("sliders")+
  theme_classic()

ggarrange(ff, si, fc, ch, cu, sl, ncol=2, nrow=3)

rm(ff, si, fc, ch, cu, sl)
```

## Distribution of Location Quality by Count

```{r distribution of location quality by count, fig.height = 8, fig.width = 8, fig.align = "left"}
zero_zero <- mlbraw2023 %>%
  filter(count == "0-0") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.01) +
  ylim(0,0.05)+
  ylab("0-0")+
  theme_classic()
zero_one <- mlbraw2023 %>%
  filter(count == "0-1") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.01) +
  ylim(0,0.05)+
  ylab("0-1")+
  theme_classic()
zero_two <- mlbraw2023 %>%
  filter(count == "0-2") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.01) +
  ylim(0,0.05)+
  ylab("0-2")+
  theme_classic()
one_zero <- mlbraw2023 %>%
  filter(count == "1-0") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.01) +
  ylim(0,0.05)+
  ylab("1-0")+
  theme_classic()
one_one <- mlbraw2023 %>%
  filter(count == "1-1") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.01) +
  ylim(0,0.05)+
  ylab("1-1")+
  theme_classic()
one_two <- mlbraw2023 %>%
  filter(count == "1-2") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.01) +
  ylim(0,0.05)+
  ylab("1-2")+
  theme_classic()
two_zero <- mlbraw2023 %>%
  filter(count == "2-0") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.01) +
  ylim(0,0.05)+
  ylab("2-0")+
  theme_classic()
two_one <- mlbraw2023 %>%
  filter(count == "2-1") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.01) +
  ylim(0,0.05)+
  ylab("2-1")+
  theme_classic()
two_two <- mlbraw2023 %>%
  filter(count == "2-2") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.01) +
  ylim(0,0.05)+
  ylab("2-2")+
  theme_classic()
three_zero <- mlbraw2023 %>%
  filter(count == "3-0") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.01) +
  ylim(0,0.05)+
  ylab("3-0")+
  theme_classic()
three_one <- mlbraw2023 %>%
  filter(count == "3-1") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.01) +
  ylim(0,0.05)+
  ylab("3-1")+
  theme_classic()
three_two <- mlbraw2023 %>%
  filter(count == "3-2") %>%
  ggplot(aes(x = lp2)) +
  geom_histogram(aes(y = after_stat(count / sum(count))), binwidth=0.01) +
  ylim(0,0.05)+
  ylab("3-2")+
  theme_classic()

ggarrange(zero_zero, zero_one, zero_two,
          one_zero, one_one, one_two,
          two_zero, two_one, two_two,
          three_zero, three_one, three_two
          , ncol=3, nrow=4)

rm(zero_zero, zero_one, zero_two,
   one_zero, one_one, one_two,
   two_zero, two_one, two_two,
   three_zero, three_one, three_two)
```

## Final Cleaning

Here is the final cleaning I'll apply to the 2023 data frame before plugging it into a dashboard and view how pitchers ranked across this new pitch location metric.

```{r create lp2_cat}
mlbraw2023 <- mlbraw2023 %>%
  mutate(lp2_cat = if_else(lp2 >= 0.85, "excellent",
                           if_else(lp2 >= 0.75, "good",
                                   if_else(lp2 >= 0.65, "average",
                                           if_else(lp2 >= 0.45, "bad",
                                                   "terrible")))))
```

```{r filter top 100 pitchers}
top100 <- mlbraw2023 %>% group_by(player_name) %>% count() %>% ungroup() %>% arrange(desc(n)) %>% head(100) %>% select(-n)
top100 <- top100$player_name

mlbraw2023 <- mlbraw2023 %>% filter(player_name %in% top100)

mlbraw2023 <- mlbraw2023 %>% 
  mutate(player_name = str_replace_all(player_name, "Su\303\241rez", "Suarez")) %>%
  mutate(player_name = str_replace_all(player_name, "Berr\303\255os, Jos\303\251", "Berrios, Jose")) %>%
  mutate(player_name = str_replace_all(player_name, "P\303\251rez, Mart\303\255n", "Perez, Martin")) %>%
  mutate(player_name = str_replace_all(player_name, "L\303\263pez", "Lopez")) %>%
  mutate(player_name = str_replace_all(player_name, "Jes\303\272s", "Jesus"))

rm(top100)
```

```{r mutate pitch type percent}
pitch_type_perc <- mlbraw2023 %>%group_by(player_name, pitch_type) %>% count() %>% ungroup() %>%
  inner_join(mlbraw2023 %>%group_by(player_name) %>% count() %>% ungroup(),
             join_by(player_name)) %>%
  mutate(pitch_type_perc = 100*round(n.x/n.y, 2)) %>%
  select(player_name, pitch_type, pitch_type_perc)

mlbraw2023 <- mlbraw2023 %>% inner_join(pitch_type_perc, join_by(player_name, pitch_type))

rm(pitch_type_perc)
```

```{r add rank to names}
mlbraw2023 <- mlbraw2023 %>%
  separate(player_name, c("name1", "name2"), ", ") %>%
  mutate(player_name = paste(name2, name1, sep = " ")) %>%
  select(player_name, pitch_type, pitch_name, count, hand, 
         plate_x, plate_z, lp2, lp2_cat, pitch_type_perc)
```

```{r add rank to names 2}
mlbraw2023 <- mlbraw2023 %>%
  group_by(player_name) %>%
  summarise(lp2=mean(lp2)) %>%
  ungroup() %>%
  arrange(desc(lp2)) %>%
  mutate(rank = row_number()) %>%
  mutate(player_rank = paste(rank, " - ", player_name)) %>%
  inner_join(mlbraw2023, join_by(player_name)) %>%
  rename(lp2 = lp2.y) %>%
  select(player_rank, player_name, pitch_type, pitch_name, count, 
         hand, plate_x, plate_z, lp2, lp2_cat, pitch_type_perc) %>%
  mutate(player_name = player_rank) %>%
  select(-player_rank)
```

```{r factor levels}
mlbraw2023$lp2_cat <- factor(mlbraw2023$lp2_cat, 
                             levels = c("excellent","good","average","bad","terrible"))
mlbraw2023$pitch_type <- factor(mlbraw2023$pitch_type, 
                                levels = c("FF","SI","FC","FS","CH","CU","SL","ST"))

mlbraw2023$pitch_name <- factor(mlbraw2023$pitch_name, 
                                levels = c("Sweeper","Slider","Curveball","Changeup",
                                           "Splitter","Cutter","Sinker","Fastball"))
```

```{r}
color_pitch <- tibble(pitch_name = unique(mlbraw2023$pitch_name),
                      colors = c("#FBB4AE","#B3CDE3","#CCEBC5","#DECBE4",
                                 "#FED9A6","#FFFFCC","#E5D8BD","#FDDAEC"))

mlbraw2023 <- mlbraw2023 %>%
  inner_join(color_pitch, join_by(pitch_name))

rm(color_pitch)

mlbraw2023$lp2 <- as.double(mlbraw2023$lp2)

text <- mlbraw2023 %>%
  group_by(player_name) %>%
  summarise(lp2= round(mean(lp2),3), .groups = 'drop')

loli <- mlbraw2023 %>%
  group_by(player_name, pitch_name, pitch_type_perc, colors) %>%
  summarise(lp2= round(mean(lp2),2), .groups = 'drop') %>%
  filter(pitch_type_perc > 2)

bar <- mlbraw2023 %>%
  select(player_name, lp2)

pie <- mlbraw2023 %>% group_by(player_name, pitch_name, colors) %>% count() %>% 
  inner_join(mlbraw2023 %>% group_by(player_name) %>% count(),
             join_by(player_name)) %>%
  mutate(p=100*round(n.x/n.y, 2)) %>%
  select(-n.x, -n.y) %>%
  filter(p > 2)
```

```{r}
write_csv(text,"/Users/dougrose/Desktop/pitch_location_quality/location_quality_app/text.csv")
write_csv(loli,"/Users/dougrose/Desktop/pitch_location_quality/location_quality_app/loli.csv")
write_csv(bar,"/Users/dougrose/Desktop/pitch_location_quality/location_quality_app/bar.csv")
write_csv(pie,"/Users/dougrose/Desktop/pitch_location_quality/location_quality_app/pie.csv")
```

```{r, echo=FALSE}
rm(text, loli, bar, pie)
```


